Reinforcement Learning for Options on Target Volatility Funds

### 2021-05-14 tex/targetvol.tex
Paper

\section{Reinforcement Learning}\label{sec:RL}
As we have discussed previously in the case of general payoffs or risky securities dynamics, one must resort to numerical approaches to solve the stochastic control problem. The standard approach could be to use classical techniques based on backwards recursion \eqref{eq:recursion}-\eqref{eq:recursion2}. However their performances may degrade as the dimension $n$ of the problem increases. In our contribution we adopt a novel technique that is gaining popularity in many scientific branches for solving stochastic optimal control problems: Reinforcement Learning.

Reinforcement Learning is a branch of Machine Learning (ML) which allows an artificial agent to interact with an environment through actions and observations in order to maximize total rewards to achieve specific goals. In RL the agent is not told which actions to take but instead it must discover by trial and error which are the behaviors yielding to the greatest reward by trying them several times. This aspect makes RL independent  from pre-collected data as other ML techniques. Because of its nature, RL has been successful in quantitative finance for solving control problems; among the most important RL applications in this field, we refer to \textcite{pioneerrlfinance} as the pioneers in studying self-taught reinforcement trading problems, while to \textcite{rlintroductionfinance} and \textcite{rlfinance} for hedging derivatives with RL under market frictions.

>>>>

\section{Reinforcement Learning}\label{sec:RL}
As we have discussed previously in the case of general payoffs or risky securities dynamics, one must resort to numerical approaches to solve the stochastic control problem related to the TVS. The standard approach could be to use classical techniques based on backwards recursion \eqref{eq:recursion}-\eqref{eq:recursion2}. However their performances may degrade as the dimension $n$ of the problem increases. In our contribution we adopt a novel technique that is gaining popularity in many scientific branches for solving stochastic optimal control problems: Reinforcement Learning.

Reinforcement Learning is a branch of Machine Learning (ML) which allows an artificial agent to interact with an environment through actions and observations in order to maximize total rewards to achieve specific goals. In RL the agent is not told which actions to take but instead it must discover by trial and error which are the behaviors yielding to the greatest reward by trying them several times. This is obtained by updating the agent policy which is  This peculiarity makes RL independent from pre-collected data as other ML techniques. Because of its nature, RL has been successful in quantitative finance for solving control problems; among the most important RL applications in this field, we refer to \textcite{pioneerrlfinance} as the pioneers in studying self-taught reinforcement trading problems, while to \textcite{rlintroductionfinance} and \textcite{rlfinance} for hedging derivatives with RL under market frictions.
